%-------------------------
% Resume in LaTeX
% Based on Jake Gutierrez's MIT-licensed resume template:
% https://github.com/jakegut/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
  \textbf{\Huge \scshape Vincenzo Rosciano} \\ \vspace{1pt}
  \small Barcelona, ES $|$ +34 657 63 25 14 $|$
  \href{mailto:vercinxd@gmail.com}{\underline{vercinxd@gmail.com}} $|$
  \href{https://www.linkedin.com/in/vincenzo-carlo-rosciano/}{\underline{LinkedIn}} $|$
  \href{https://github.com/vercinbleach}{\underline{GitHub}}
\end{center}

\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Canterbury Christ Church University}{Expected graduation: 2027}
      {BSc in Computer Science}{}
    \resumeSubheading
      {iFP Grupo Planeta}{Barcelona, ES}
      {CFGS Higher National Diploma, Web Application Developer}{Graduated: 2023}
    \resumeSubheading
      {La Salle La Colina}{Caracas, VE}
      {GED}{Graduated: 2019}
  \resumeSubHeadingListEnd

\section{EXPERIENCE}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lead Developer}{Jan. 2026 - Present}
      {Grup Montaner}{Barcelona, ES}
      \resumeItemListStart
        \resumeItem{Lead a three-person development team, managing two developers and using GitHub Projects to prioritize, assign, and track delivery across the Operations App and internal Camunda platform.}
        \resumeItem{Coordinate a GitFlow-based delivery model with main, develop, work branches, and pull requests, aligning parallel development with controlled integration.}
      \resumeItemListEnd
    \resumeSubheading
      {Software Engineer}{July 2025 - Dec. 2025}
      {Grup Montaner}{Barcelona, ES}
      \resumeItemListStart
        \resumeItem{Architected a full-stack BPM platform for a EUR 90M-revenue organization using an open-source Java engine and Next.js/React to centralize cross-department workflows.}
        \resumeItem{Built Java/Python microservices and an RPA layer for CRM synchronization, compliance workflows, and an API-less legacy ERP, while delivering executive Power BI dashboards.}
      \resumeItemListEnd
    \resumeSubheading
      {Software Engineer}{Sept. 2024 - July 2025}
      {Neverhack}{Barcelona, ES}
      \resumeItemListStart
        \resumeItem{Delivered 10+ Splunk SOAR playbooks with Python and Bash for automated IP blocking and remediation, saving 20+ hours weekly and EUR 34K annually.}
      \resumeItemListEnd
    \resumeSubheading
      {Junior Software Engineer}{May 2023 - Sept. 2024}
      {Innovery}{Barcelona, ES}
      \resumeItemListStart
        \resumeItem{Rewrote 90\% of the logic across 10+ critical workflows in a legacy no-code platform, reducing incidents from 10 per week to 3 per month and clearing the backlog.}
        \resumeItem{Built an integration ecosystem across 10+ platforms, including CRM, ERP, LinkedIn, and Microsoft 365, automating CRM-ERP synchronization and reducing data silos.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{PROJECTS}
  \resumeSubHeadingListStart
    \resumeProjectHeading
      {\textbf{Editify - Voice x Fintech Hackathon} $|$ \href{https://github.com/vercinbleach/hackaton-cala-voice-of-finance}{\underline{GitHub}}}{}
      \resumeItemListStart
        \resumeItem{Built a multi-agent financial video editor in one night as the sole developer on a three-person team with two non-technical collaborators, orchestrating Cala, Codex, ElevenLabs, HyperFrames, and FFmpeg.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{AI-Powered Mortgage Agent}}{}
      \resumeItemListStart
        \resumeItem{Collaborated in a three-person team on an AI agent for the Spanish mortgage market, using Selenium, OCR, LangChain, and LLMs to structure data from major banks with 100\% accuracy in weekly market updates.}
      \resumeItemListEnd
    \resumeProjectHeading
      {\textbf{SuiteCRM Open Source} $|$ \href{https://github.com/SuiteCRM/SuiteCRM/pull/10766}{\underline{Open PR}}}{}
      \resumeItemListStart
        \resumeItem{Extended the V8 JSON API with base64 DocumentRevision uploads, extension validation, and MIME metadata; some users sent thanks years later.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{TECHNICAL SKILLS}
  \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
      \textbf{Backend}{: Microservices, Python, FastAPI, Java, Spring Boot, PHP, MySQL, PostgreSQL} \\
      \textbf{Frontend}{: React, Next.js, TypeScript, Tailwind CSS, shadcn/ui} \\
      \textbf{Tools}{: Docker, AWS, Git, Linux, CI/CD, Splunk SOAR, Bash, Power BI} \\
      \textbf{AI}{: LLMs, Agent Orchestration, Tool Calling, Agent Harnesses, LLM-as-Judge} \\
      \textbf{Languages}{: Spanish (native), English (fluent), Italian (fluent)}
    }}
  \end{itemize}

\end{document}
